\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{authblk}
\usepackage[hidelinks]{hyperref}
\renewcommand\Affilfont{\itshape\small}
\begin{document}

% ============================================================
% TITLE PAGE (submitted separately; NOT part of the anonymized manuscript)
% Journal: Food Policy
% ============================================================

\title{\textbf{Hybrid Gains and Tasty Grains: Comparing Production- and
Consumption-Focused Seed Promotion Strategies to Accelerate Varietal Turnover}}

\author[1]{Bjorn Van Campenhout\thanks{Corresponding author.
Email: \texttt{b.vancampenhout@cgiar.org}.}}
\author[2]{Leocardia Nabwire}
\author[3]{Berber Kramer}
\author[4]{Carly Trachtman}
\author[4]{Gashaw T. Abate}

\affil[1]{Innovation Policy and Scaling Unit, International Food Policy Research
Institute (IFPRI), Leuven, Belgium}
\affil[2]{One Acre Fund, Jinja, Uganda}
\affil[3]{Markets, Trade and Institutions Unit, International Food Policy Research
Institute (IFPRI), Nairobi, Kenya}
\affil[4]{Markets, Trade and Institutions Unit, International Food Policy Research
Institute (IFPRI), Washington, DC, USA}

\date{}
\maketitle

\vfill

\section*{Acknowledgments}

This research received clearance from Makerere's School of Social Sciences
Research Ethics Committee (MAKSSREC 01.23.627/PR1) as well as from the IFPRI
Institutional Review Board (DSGD-23-0108). The research was registered with the
Ugandan National Council for Science and Technology (SS1657ES) and at the
American Economic Association (AEA) RCT Registry (AEARCTR-0010666).

We thank Richard Ariong, Wilberforce Walukano, and Marc Charles Wanume for field
support. This work is part of a broader set of coordinated trials testing similar
interventions (seed trial packs and a consumer-focused intervention) in different
contexts across six sites (Trachtman et al., 2023). We are also indebted to the
CGIAR Market Intelligence Work Package 3 team---Julius Juma Okello, Beliyou Haile,
Martina Cavicchioli, Prakashan Chellattan Veettil, Vikram Patil, Maya Moore, and
Catherine Ragasa---for comments and suggestions.

\section*{Funding}

We thank all funders who support this research through their contributions to the
CGIAR Trust Fund (\url{https://www.cgiar.org/funders/}). In particular, funding
from the CGIAR Initiative on Market Intelligence and the CGIAR Initiative on
SeedEqual is gratefully acknowledged.

\section*{Declaration of generative AI in the writing process}

During the preparation of this work the authors used OpenAI and Anthropic models
to obtain editorial suggestions to improve clarity and readability and to explore
alternative phrasing for technical terms. After using these tools, the authors
reviewed and edited the content as needed and take full responsibility for the
content of the article.

\section*{Declaration of competing interest}

The authors declare that they have no known competing financial interests or
personal relationships that could have appeared to influence the work reported in
this paper.

\section*{Data and code availability}

Data and replication code are available at
\url{https://github.com/bjvca/mippi_UG}.

\end{document}
